Loop Invariant Code Motion in PyPy's Tracing JIT

### 2011-06-15 talk/iwtc11/paper.tex
fix h?kan's name
an XXX

\authorinfo{Hakan Ardo XXX}
           {Centre for Mathematical Sciences, Lund University}
           {hakan@debian.org}
\authorinfo{Carl Friedrich Bolz}
           {Heinrich-Heine-Universität Düsseldorf}
           {cfbolz@gmx.de}
\authorinfo{Maciej Fijałkowski}
           {Affiliation2}
           {fijall@gmail.com}

@@

\section{Optimizations}
Before the trace is passed to a backend compiling it into machine code
it needs to be optimized to achieve better performance.
The focus of this paper
is loop invariant code motion. The goal of that is to move as many
operations as possible out of the loop making them executed at most once
and not every iteration. This we propose to achieve by loop peeling. It
leaves the loop body intact, but prefixes it with one iteration of the
loop. This operation by itself will not achieve anything. But if it is
combined with other optimizations it can increase the effectiveness of
those optimizations. For many optimization of interest some care has
to be taken when they are combined with loop peeling. This is
described below by first explaining the loop peeling optimization
followed by a set of other optimizations and how they interact with
loop peeling.

>>>>

\authorinfo{H\aa kan Ardö}
           {Centre for Mathematical Sciences, Lund University}
           {hakan@debian.org}
\authorinfo{Carl Friedrich Bolz}
           {Heinrich-Heine-Universität Düsseldorf}
           {cfbolz@gmx.de}
\authorinfo{Maciej Fijałkowski}
           {Affiliation2}
           {fijall@gmail.com}

@@

\section{Trace Optimizations}

XXX make clear that the preamble is not necessarily the \emph{first} iteration
of a loop

Before the trace is passed to a backend compiling it into machine code
it needs to be optimized to achieve better performance.
The focus of this paper
is loop invariant code motion. The goal of that is to move as many
operations as possible out of the loop making them executed at most once
and not every iteration. This we propose to achieve by loop peeling. It
leaves the loop body intact, but prefixes it with one iteration of the
loop. This operation by itself will not achieve anything. But if it is
combined with other optimizations it can increase the effectiveness of
those optimizations. For many optimization of interest some care has
to be taken when they are combined with loop peeling. This is
described below by first explaining the loop peeling optimization
followed by a set of other optimizations and how they interact with
loop peeling.
